Wastewater Example Datasets

```{r lib}
library(data.table)
```


Let's investigate the quality of all MAGs

```{r readInRemoteFiles}
all_files = c(
"https://openstack.cebitec.uni-bielefeld.de:8080/wastewater-test2/ERR2592245/1/magAttributes/1.0.1/checkm/ERR2592245_checkm_G5cnwW9c.tsv",
"https://openstack.cebitec.uni-bielefeld.de:8080/wastewater-test2/ERR2592249/1/magAttributes/1.0.1/checkm/ERR2592249_checkm_lGLjemNy.tsv",
"https://openstack.cebitec.uni-bielefeld.de:8080/wastewater-test2/ERR2592251/1/magAttributes/1.0.1/checkm/ERR2592251_checkm_NReHTBxy.tsv",
"https://openstack.cebitec.uni-bielefeld.de:8080/wastewater-test2/ERR2592252/1/magAttributes/1.0.1/checkm/ERR2592252_checkm_ALtKuhvK.tsv",
"https://openstack.cebitec.uni-bielefeld.de:8080/wastewater-test2/ERR2592253/1/magAttributes/1.0.1/checkm/ERR2592253_checkm_8jPgQr9a.tsv")



# empty list to store each file as a data.frame when read-in
file_list <- vector(mode="list", length=length(all_files))

# loop over files, reading in one at a time
for(i in 1:length(all_files)) {
    file_list[[i]] <- read.csv(all_files[i], sep = '\t')
}

# stack all of the files using rbindlist() from package data.table
big_df <- rbindlist(file_list)
